Figures from: Vertebrate host availability and the thermal properties of mosquito-borne parasite transmission

### 2023-05-11 manuscript-figures.Rmd
add updated figure code to Rmd
remains to:
* re-calculate R0 values with enough resolution to plot heatmap
* re-create persistence threshold figures (CTmin/max vs. CHmin/max)

@@

# R0 data
data.R0 <- read_rds("results/R0_vals.rds")
# Topt data
data.Topt <- read_rds("results/Topt_vals.rds")
# Critical thermal extrema data
data.CT <- read_rds("results/CT_vals.rds")

@@

```{r plot-settings, include = FALSE}
# Set theme
theme_set(theme_minimal(11))

  lemon::reposition_legend(p, "center", panel = names(pnls))
}
```

@@

## Configure data frame for plotting
R0_df <- AllOutputs %>%
  select(system_ID, system_label, Temperature, sigmaH, KH, R0) %>%
  # Consider only 3 values of KH (on a log10-scale)
  filter(KH %in% c(1E-1, 1E0, 1E1)) %>%
  # Choose a limited range of sigmaH values
  filter(sigmaH > 10^0.5) %>%
  # Group by plotting variables
  group_by(system_ID, KH, sigmaH) %>%
  # Calculate Topt (which.max requires grouping)
  mutate(Topt = `Temperature`[which.max(R0)]) %>%
  as_tibble() %>%
  arrange(system_ID, sigmaH, Temperature)

@@

```{r fig-S2_Topt_plots_varyKH, dev = c('pdf','svg', 'tiff'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:Topt_plots_varyKH} The thermal optimum for transmission, $T_{opt}$, may be sensitive to vertebrate host population density and biting tolerance.'}

Topt_df <- ThermPathChars %>%
  filter(KH > 0.01) %>%
  filter(sigmaH %in% 10^seq(0, 2) | is.infinite(sigmaH)) %>%
  group_by(KH) %>%
  # Arrange along the plotting variables
  arrange(system_ID, KH, Topt) %>%
  arrange(sigmaH) %>%
  ungroup()

Topt_plots <- Topt_df %>%
  ## Set up plot ##
  # x = blood meal supply, y = thermal optimum,
  # color = sigmaH
  ggplot(aes(
    x = KH, y = Topt,
    colour = as.factor(sigmaH)
  )) +

  # Topt curves:
  geom_path(lwd = 1) +

  # x-axis: log10 scale, no buffer space
  scale_x_log10(
    name = TeX("Vertebrate host population density (ind/ha)"),
    expand = c(0, 0),
    limits = c(0.01, 2E4),
    breaks = 10^seq(-2, 4),
    labels = TeX(c(
      "0.01", "0.1", "$1$", "$10$", "$100$", "$10^3$", "$10^4$"
    ))
  ) +

  # y-axis
  scale_y_continuous(
    name = expression("Thermal optimum "(degree * C)),
    expand = c(0.05, 0.05),
    limits = range(ThermPathChars$Topt),
    breaks = seq(floor(range(ThermPathChars$Topt)[1]),
                 floor(range(ThermPathChars$Topt)[2]),
                 by = 1
    )
  ) +
  # color:
  scale_colour_manual(
    name = "Vertebrate host biting tolerance\n(bites per host per day)",
    values = c(met.brewer("VanGogh3", 3, direction = 1), "black"),
    # values = c(brewer.pal(9, "YlOrRd")[c(3, 5, 7)], "black"),
    breaks = c(1, 10, 100, Inf),
    labels = unname(c("1 (Chitnis)", "10 (Chitnis)", "100 (Chitnis)", TeX("$\\infty$ (Ross-Macdonald)")))
  ) +

  # theme options:
  theme_minimal_hgrid(11) +
  guides(color = guide_legend(override.aes = list(size = 4))) +
  theme(
    legend.position = "bottom",
    legend.margin = margin(),
    legend.direction = "vertical",
    legend.title = element_text(size = 10),
    legend.text = element_text(
      size = 10,
      hjust = 0
    ),
    legend.justification = "left",
    axis.title.x = element_text(hjust = 0.5),
    strip.text = ggtext::element_markdown(
      size = 11,
      hjust = 0,
      padding = margin(0, 0, 0, 0),
      margin = margin(1, 1, 1, 1)
    )
  )

# Plot
shift_legend(Topt_plots)

@@

Topt_df <- ThermPathChars %>%
  # Choose appropriate pop. dens. values and group
  filter(KH %in% 10^seq(0, 4)) %>%
  group_by(KH) %>%
  # Arrange along the plotting variables
  arrange(system_ID, sigmaH, Topt) %>%
  arrange(KH) %>%
  ungroup()

Topt_plots <- Topt_df %>%
  ## Set up plot ##
  # x-axis = vertebrate host biting tolerance, y-axis = thermal optimum,
  # color = vertebrate host population density
  ggplot(aes(x = sigmaH_proxy, y = Topt, colour = as.factor(KH))) +

  # Topt curves:
  geom_path(lwd = 2) +

  # white lines breaking up finite/infinite sigmaH values:
  geom_vline(
    aes(xintercept = 0.95 * infinite_divide),
    colour = "white",
    lwd = .9,
    show.legend = FALSE
  ) +
  geom_vline(
    aes(xintercept = 1.05 * infinite_divide),
    colour = "white",
    lwd = .9,
    show.legend = FALSE
  ) +
  geom_vline(
    aes(xintercept = 1.15 * infinite_divide),
    colour = "white",
    lwd = .9,
    show.legend = FALSE
  ) +

  # x-axis: Use a log10-scale with no buffer space
  scale_x_log10(
    name = TeX("Vertebrate host biting tolerance (bites per host per day)"),
    expand = c(0, 0),
    limits = c(5, 3500),
    breaks = sigmaH_breaks,
    labels = sigmaH_labels
  ) +

  # y-axis: Set limits and breaks and add some buffer space
  scale_y_continuous(
    name = expression("Thermal optimum "(degree * C)),
    expand = c(0.05, 0.05),
    limits = range(ThermPathChars$Topt),
    breaks = seq(floor(range(ThermPathChars$Topt)[1]),
                 floor(range(ThermPathChars$Topt)[2]),
                 by = 1
    )
  ) +

  # color:
  scale_colour_manual(
    name = "Vertebrate host population\ndensity (ind/ha)",
    values = met.brewer("Hokusai3", 5),
    # option = "plasma"
  ) +

  # faceting:
  facet_wrap(~system_label, scales = "free", nrow = 2, labeller = labeller()) +

  # theme options:
  theme_minimal_hgrid(11) +
  guides(color = guide_legend(override.aes = list(size = 4))) +
  theme(
    legend.position = "bottom",
    legend.margin = margin(),
    legend.direction = "vertical",
    legend.justification = "center",
    axis.title.x = element_text(hjust = 0.5),
    strip.text = ggtext::element_markdown(
      size = 11,
      hjust = 0,
      padding = margin(0, 0, 0, 0),
      margin = margin(1, 1, 1, 1)
    )
  )

# Plot
shift_legend(Topt_plots)
```

@@

CTmin_df <- ThermPathChars %>%
  ungroup() %>%
  distinct() %>%
  # Arrange along the plotting variables
  arrange(system_label, sigmaH_proxy, KH, CTmin)

# add many proxy sigmaH points at infinity to make the values easier to see there
temp <- filter(CTmin_df, is.infinite(sigmaH)) %>%
  mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH,
                               mean(c(1.25 * infinite_divide, infinite_skew))
  ))
temp2 <- filter(CTmin_df, is.infinite(sigmaH)) %>%
  mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH,
                               mean(c(1.15 * infinite_divide, infinite_skew))
  ))
temp3 <- filter(CTmin_df, is.infinite(sigmaH)) %>%
  mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH,
                               mean(c(1.05 * infinite_divide, infinite_skew))
  ))
temp4 <- filter(CTmin_df, is.infinite(sigmaH)) %>%
  mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH,
                               mean(c(1.3 * infinite_divide, infinite_skew))
  ))
temp5 <- filter(CTmin_df, is.infinite(sigmaH)) %>%
  mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH,
                               mean(c(1.2 * infinite_divide, infinite_skew))
  ))
temp6 <- filter(CTmin_df, is.infinite(sigmaH)) %>%
  mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH,
                               mean(c(1.1 * infinite_divide, infinite_skew))
  ))
temp7 <- filter(CTmin_df, is.infinite(sigmaH)) %>%
  mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH,
                               mean(c(infinite_divide, infinite_skew))
  ))

@@

CTmin_breaks <- seq(15, 31, by = 1)

CTmin_plots <- CTmin_df %>%
  ## Set up plot ##
  # x = biting tolerance (with a point at infinity),
  # y = vertebrate host population density,
  # color = transmission thermal optimum
  ggplot(aes(x = KH, y = sigmaH_proxy)) +

  # CTmin for FINITE sigmaH:
  geom_contour_filled(
    data = filter(CTmin_df, sigmaH_proxy < infinite_divide**0.98),
    aes(z = CTmin),
    breaks = CTmin_breaks
  ) +

  # CTmin for INFINITE sigmaH:
  geom_contour_filled(
    data = filter(CTmin_df, sigmaH_proxy > infinite_divide**1.02),
    aes(z = CTmin),
    size = 1,
    breaks = CTmin_breaks
  ) +

  # x-axis: log10-scale with no buffer space
  scale_x_log10(
    name = TeX("Vertebrate host population density (ind/ha)"),
    expand = c(0, 0),
    limits = c(0.05, 1E4),
    breaks = 10^seq(-1, 4, 1),
    labels = TeX(c("$0.1$", "$1$", "$10", "$100$", "$10^3$", "$10^4$"))
  ) +
  # y-axis: log10-scale y axis, with no buffer space
  scale_y_log10(
    name = TeX("Biting tolerance (bites per host per day)"),
    expand = c(0, 0),
    breaks = sigmaH_breaks,
    labels = sigmaH_labels
  ) +

  # fill:
  scale_fill_viridis_d(
    name = "Critical thermal minimum (°C)"
  ) +

  # faceting:
  facet_wrap(~system_label, scales = "free", nrow = 2, labeller = labeller()) +

  # legend:
  guides(fill = guide_coloursteps(
    title.position = "top",
    title.hjust = 0.5,
    direction = "vertical",
    barheight = unit(6, "cm"),
    show.limits = TRUE
  )) +

  # theme options:
  theme_minimal(11) +
  theme(
    plot.title = ggtext::element_markdown(),
    legend.position = "right",
    legend.margin = margin(0, 0, 0, 0),
    legend.text = element_text(size = 11),
    legend.title = element_text(size = 11, hjust = 0),
    legend.direction = "horizontal",
    legend.justification = "left",
    axis.title.x = element_text(hjust = 0.5),
    strip.text = ggtext::element_markdown(
      size = 11,
      hjust = 0,
      padding = margin(0, 0, 0, 0)
    )
  )

# Plot
shift_legend(CTmin_plots)
```

@@

CTmax_df <- ThermPathChars %>%
  ungroup() %>%
  distinct() %>%
  # Arrange along the plotting variables
  arrange(system_label, sigmaH_proxy, KH, CTmin)

# add many proxy sigmaH points at infinity to make the values easier to see there
temp <- filter(CTmax_df, is.infinite(sigmaH)) %>%
  mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH,
                               mean(c(1.25 * infinite_divide, infinite_skew))
  ))
temp2 <- filter(CTmax_df, is.infinite(sigmaH)) %>%
  mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH,
                               mean(c(1.15 * infinite_divide, infinite_skew))
  ))
temp3 <- filter(CTmax_df, is.infinite(sigmaH)) %>%
  mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH,
                               mean(c(1.05 * infinite_divide, infinite_skew))
  ))
temp4 <- filter(CTmax_df, is.infinite(sigmaH)) %>%
  mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH,
                               mean(c(1.3 * infinite_divide, infinite_skew))
  ))
temp5 <- filter(CTmax_df, is.infinite(sigmaH)) %>%
  mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH,
                               mean(c(1.2 * infinite_divide, infinite_skew))
  ))
temp6 <- filter(CTmax_df, is.infinite(sigmaH)) %>%
  mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH,
                               mean(c(1.1 * infinite_divide, infinite_skew))
  ))
temp7 <- filter(CTmax_df, is.infinite(sigmaH)) %>%
  mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH,
                               mean(c(infinite_divide, infinite_skew))
  ))

@@

CTmax_breaks <- seq(23, 35, by = 1)

CTmax_plots <- CTmax_df %>%
  ## Set up plot ##
  # x = biting tolerance (with a point at infinity),
  # y = vertebrate host population density,
  # color = transmission thermal optimum
  ggplot(aes(x = KH, y = sigmaH_proxy)) +

  # CTmin for FINITE sigmaH:
  geom_contour_filled(
    data = filter(CTmax_df, sigmaH_proxy < infinite_divide**0.98),
    aes(z = CTmax),
    breaks = CTmax_breaks
  ) +

  # CTmin for INFINITE sigmaH:
  geom_contour_filled(
    data = filter(CTmax_df, sigmaH_proxy > infinite_divide**1.02),
    aes(z = CTmax),
    size = 1,
    breaks = CTmax_breaks
  ) +

  # x-axis: log10-scale with no buffer space
  scale_x_log10(
    name = TeX("Vertebrate host population density (ind/ha)"),
    expand = c(0, 0),
    limits = c(0.05, 1E4),
    breaks = 10^seq(-1, 4, 1),
    labels = TeX(c("$0.1$", "$1$", "$10", "$100$", "$10^3$", "$10^4$"))
  ) +
  # y-axis: log10-scale y axis, with no buffer space
  scale_y_log10(
    name = TeX("Biting tolerance (bites per host per day)"),
    expand = c(0, 0),
    breaks = sigmaH_breaks,
    labels = sigmaH_labels
  ) +

  # fill:
  scale_fill_manual(
    name = "Critical thermal maximum (°C)",
    values = met.brewer("Tam",
                        n = length(CTmax_breaks),
                        direction = -1
    )
  ) +

  # faceting:
  facet_wrap(~system_label, scales = "free", nrow = 2, labeller = labeller()) +

  # legend:
  guides(fill = guide_coloursteps(
    title.position = "top",
    title.hjust = 0.5,
    direction = "vertical",
    barheight = unit(6, "cm"),
    show.limits = TRUE
  )) +

  # theme options:
  theme_minimal(11) +
  theme(
    plot.title = ggtext::element_markdown(),
    legend.position = "right",
    legend.margin = margin(0, 0, 0, 0),
    legend.text = element_text(size = 11),
    legend.title = element_text(size = 11, hjust = 0),
    legend.direction = "horizontal",
    legend.justification = "left",
    axis.title.x = element_text(hjust = 0.5),
    strip.text = ggtext::element_markdown(
      size = 11,
      hjust = 0,
      padding = margin(0, 0, 0, 0)
    )
  )

# Plot
shift_legend(CTmax_plots)
```

>>>>

# Plot settings ----

# Set theme
theme_set(theme_minimal(11))

  lemon::reposition_legend(p, "center", panel = names(pnls))
}

@@

# R0 data
data.R0 <- read_rds("results/R0_vals.rds") # !!! needs to be updated to include 1e-1, 1e0, 1e1
# Topt data
data.Topt <- read_rds("results/Topt_vals.rds")
# Critical thermal extrema data
data.CT <- read_rds("results/CT_vals.rds")

@@

@@

## Configure data frame for plotting
R0_df <- data.R0 %>%
  select(system_ID, system_label, Temperature, sigmaH, KH, median) %>%
  rename(R0 = median) %>% 
  # Consider only 3 values of KH (on a log10-scale)
  filter(KH %in% c(1E-1, unique(data.R0$KH)[7], unique(data.R0$KH)[10])) %>% # !!! temporary. recalculate R0 with 1e-1, 1e0, 1e1
  # Choose a limited range of sigmaH values
  filter(sigmaH > 10^0.5) %>%
  # Group by plotting variables
  group_by(system_ID, KH, sigmaH) %>%
  # Calculate Topt (which.max requires grouping)
  mutate(Topt = `Temperature`[which.max(R0)]) %>%
  as_tibble() %>%
  arrange(system_ID, sigmaH, Temperature)

@@

```{r fig-S2_Topt_plots_varyKH, dev = c('pdf','svg', 'tiff'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:Topt_plots_varyKH} The thermal optimum for transmission, $T_{opt}$, may be sensitive to vertebrate host population density and biting tolerance.'}
Topt_df <- data.Topt %>% 
  pivot_wider(id_cols = c("system_ID", "Model", "sigmaH", "KH"), 
              names_from = variable,
              values_from = c("mean", "median", "lowHCI", "highHCI"))  %>% 
  right_join(read_rds("results/CT_vals.rds") %>% 
               filter(variable == "CTwidth") %>% 
               pivot_wider(id_cols = c("system_ID", "Model", "sigmaH", "KH"), 
                           names_from = "variable",
                           values_from = c("mean", "median", "lowHCI", "highHCI"))) %>% 
  filter(sigmaH %in% c(1, 10, 100, Inf)) %>% 
  # filter(mean_CTwidth>0) %>% 
  select(-c(mean_CTwidth, median_CTwidth, lowHCI_CTwidth, highHCI_CTwidth)) %>%
  rename(mean = mean_Topt, median = median_Topt, lowHCI = lowHCI_Topt, 
         highHCI = highHCI_Topt) %>% 
  # filter(KH > 0.01) %>%
  # filter(sigmaH %in% 10^seq(0, 2) | is.infinite(sigmaH)) %>%
  group_by(KH) %>%
  # Arrange along the plotting variables
  arrange(system_ID, KH, mean) %>%
  arrange(sigmaH) %>%
  ungroup()

# PLOTTING
Topt_plot <- Topt_df %>%
  ## Set up plot ##
  # color = sigmaH
  ggplot(aes(x = KH, colour = as.factor(sigmaH))) +
  # Topt curves:
  geom_path(aes(y = median), lwd = 1) +
  # # Add dotted lines showing 89% HCI limits
  # geom_path(aes(y = lowHCI), linetype = "dashed") +
  # geom_path(aes(y = highHCI), linetype = "dashed") +
  # x-axis: log10 scale, no buffer space
  scale_x_log10(
    name = TeX("Vertebrate host population density (ind/ha)"),
    expand = c(0, 0),
    limits = c(0.01, 2E4),
    breaks = 10^seq(-2, 4),
    labels = TeX(c(
      "0.01", "0.1", "$1$", "$10$", "$100$", "$10^3$", "$10^4$"
    ))
  ) +
  # y-axis
  scale_y_continuous(
    name = expression("Thermal optimum "(degree * C)),
    expand = c(0.05, 0.05),
    limits = c(21,30.5), # mean: 21-31, median: 21-32
    breaks = seq(21,32, by = 1)
  ) +
  # color:
  scale_colour_manual(
    name = "Vertebrate host biting tolerance\n(bites per host per day)",
    values = c(met.brewer("VanGogh3", 4, direction = 1), "black"),
    # values = c(brewer.pal(9, "YlOrRd")[c(3, 5, 7)], "black"),
    breaks = c(1, 10, 100, Inf),
    labels = unname(c("1 (Chitnis)", "10 (Chitnis)", "100 (Chitnis)", TeX("$\\infty$ (Ross-Macdonald)")))
  ) +
  scale_fill_manual(
    name = "Vertebrate host biting tolerance\n(bites per host per day)",
    values = c(met.brewer("VanGogh3", 4, direction = 1), "black"),
    # values = c(brewer.pal(9, "YlOrRd")[c(3, 5, 7)], "black"),
    breaks = c(1, 10, 100, Inf),
    labels = unname(c("1 (Chitnis)", "10 (Chitnis)", "100 (Chitnis)", TeX("$\\infty$ (Ross-Macdonald)")))
  ) +
  # faceting:
  facet_wrap(~system_ID, nrow = 2, labeller = labeller()) +
  # theme options:
  theme_minimal(16) +
  guides(color = guide_legend(override.aes = list(size = 4))) +
  theme(
    legend.position = "bottom",
    legend.margin = margin(),
    legend.direction = "vertical",
    legend.title = element_text(size = 10),
    legend.text = element_text(
      size = 10,
      hjust = 0
    ),
    legend.justification = "left",
    axis.title.x = element_text(hjust = 0.5),
    strip.text = ggtext::element_markdown(
      size = 11,
      hjust = 0,
      padding = margin(0, 0, 0, 0),
      margin = margin(1, 1, 1, 1)
    )
  )

# Plot
Topt_plot <- shift_legend(Topt_plot)
```

@@

Topt_plot <- data.Topt %>% 
  # filter(sigmaH %in% c(1, 10, 100, Inf)) %>% 
  # Choose appropriate pop. dens. values and group
  filter(KH %in% 10^seq(0, 3)) %>%
  arrange(system_ID, KH, sigmaH, median) %>% 
  ## Set up plot ##
  # color = sigmaH
  ggplot(aes(x = sigmaH, colour = as.factor(KH))) +
  # Topt curves:
  geom_path(aes(y = mean), lwd = 1) +
  # # Dotted lines showing limits of 89% HCI
  # geom_path(aes(y = lowHCI),linetype = "dashed") +
  # geom_path(aes(y = highHCI),linetype = "dashed") +
  # white lines breaking up finite/infinite sigmaH values:
  geom_vline(
    aes(xintercept = 0.95 * infinite_divide),
    colour = "white",
    lwd = .9,
    show.legend = FALSE
  ) +
  geom_vline(
    aes(xintercept = 1.05 * infinite_divide),
    colour = "white",
    lwd = .9,
    show.legend = FALSE
  ) +
  geom_vline(
    aes(xintercept = 1.15 * infinite_divide),
    colour = "white",
    lwd = .9,
    show.legend = FALSE
  ) +
  # x-axis: Use a log10-scale with no buffer space
  scale_x_log10(
    name = TeX("Vertebrate host biting tolerance (bites per host per day)"),
    expand = c(0, 0),
    limits = c(0.5, 150),
    breaks = sigmaH_breaks,
    labels = sigmaH_labels
  ) +
  # y-axis
  scale_y_continuous(
    name = expression("Thermal optimum "(degree * C)),
    expand = c(0.05, 0.05),
    limits = c(21,31), # mean: 21-31, median: 21-32
    breaks = seq(21,32, by = 1)
  ) +
  # color:
  scale_colour_manual(
    name = "Vertebrate host population\ndensity (ind/ha)",
    values = met.brewer("Hokusai3", 4,
                        # option = "plasma"
    )) +
  scale_fill_manual(
    name = "Vertebrate host population\ndensity (ind/ha)",
    values = met.brewer("Hokusai3", 4,
                        # option = "plasma"
    )) +
  # faceting:
  facet_wrap(~system_ID,
             scales = "free",
             nrow = 2,
             labeller = labeller()  ) +
  # theme options:
  theme_minimal(16) +
  guides(color = guide_legend(override.aes = list(size = 4))) +
  theme(
    legend.position = "bottom",
    legend.margin = margin(),
    legend.direction = "vertical",
    legend.title = element_text(size = 10),
    legend.text = element_text(
      size = 10,
      hjust = 0
    ),
    legend.justification = "left",
    axis.title.x = element_text(hjust = 0.5),
    strip.text = ggtext::element_markdown(
      size = 11,
      hjust = 0,
      padding = margin(0, 0, 0, 0),
      margin = margin(1, 1, 1, 1)
    )
  )

# Plot
Topt_plot <- shift_legend(Topt_plot)
```

@@

CTmin_df <- data.CT %>%
  filter(variable == "CTmin") %>% 
  filter(is.finite(mean)) %>%
  mutate(sigmaH_proxy = sigmaH) %>% 
  # Arrange along the plotting variables
  arrange(system_ID, KH, sigmaH_proxy, mean) %>% 
  ungroup()

# add many third proxy sigmaH points at infinity to make the values easier to see there
temp <- filter(CTmin_df, is.infinite(sigmaH)) %>%
  mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH,
                               mean(c(1.25 * infinite_divide, infinite_skew))
  ))
temp2 <- filter(CTmin_df, is.infinite(sigmaH)) %>%
  mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH,
                               mean(c(1.15 * infinite_divide, infinite_skew))
  ))
temp3 <- filter(CTmin_df, is.infinite(sigmaH)) %>%
  mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH,
                               mean(c(1.05 * infinite_divide, infinite_skew))
  ))
temp4 <- filter(CTmin_df, is.infinite(sigmaH)) %>%
  mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH,
                               mean(c(1.3 * infinite_divide, infinite_skew))
  ))
temp5 <- filter(CTmin_df, is.infinite(sigmaH)) %>%
  mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH,
                               mean(c(1.2 * infinite_divide, infinite_skew))
  ))
temp6 <- filter(CTmin_df, is.infinite(sigmaH)) %>%
  mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH,
                               mean(c(1.1 * infinite_divide, infinite_skew))
  ))
temp7 <- filter(CTmin_df, is.infinite(sigmaH)) %>%
  mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH,
                               mean(c(infinite_divide, infinite_skew))
  ))

@@

CTmin_heat_plots <- CTmin_df %>%
  ## Set up plot ##
  # x = biting tolerance (with a point at infinity),
  # y = vertebrate host population density,
  # color = width of parasite thermal mean_CTwidth
  ggplot(aes(x = KH, y = sigmaH_proxy, z = median)) +

  # CTmin for FINITE sigmaH:
  geom_contour_filled(
    data = filter(CTmin_df, sigmaH_proxy < 100)
  ) +

  # CTmin for INFINITE sigmaH:
  geom_contour_filled(
    data = filter(CTmin_df, is.infinite(sigmaH))
  ) +

  # x-axis: log10-scale with no buffer space
  scale_x_log10(
    name = TeX("Vertebrate host population density (ind/ha)"),
    expand = c(0, 0),
    limits = c(0.05, 1E4),
    breaks = 10^seq(-1, 4, 1),
    labels = TeX(c("$0.1$", "$1$", "$10", "$100$", "$10^3$", "$10^4$"))
  ) +
  # y-axis: log10-scale y axis, with no buffer space
  scale_y_log10(
    name = TeX("Biting tolerance (bites per host per day)"),
    expand = c(0, 0),
    breaks = sigmaH_breaks,
    labels = sigmaH_labels
  ) +
  # color:
  scale_fill_viridis_d(
    name = "Mean critical thermal minimum (°C)",
    option = "plasma"
  ) +
  # faceting:
  facet_wrap(~system_ID, scales = "free", nrow = 2, labeller = labeller()) +
  # legend:
  guides(fill = guide_coloursteps(
    title.position = "top", title.hjust = 0.5,
    barwidth = unit(10, "cm"),
    show.limits = TRUE
  )) +
  # theme options:
  theme_minimal(16) +
  theme(
    legend.box = "horizontal",
    legend.position = "bottom",
    legend.margin = margin(0, 0, 0, 0),
    legend.title = element_text(size = 10),
    legend.direction = "horizontal",
    legend.justification = "left",
    axis.title.x = element_text(hjust = 0.5),
    strip.text = ggtext::element_markdown(
      size = 11,
      hjust = 0,
      padding = margin(0, 0, 0, 0),
      margin = margin(1, 1, 1, 1)
    )
  )

# Plot
CTmin_heat_plots <- shift_legend(CTmin_heat_plots)
```

@@

CTmax_df <- read_rds("results/CT_vals.rds") %>%
  filter(variable == "CTmax") %>% 
  filter(is.finite(mean)) %>%
  mutate(sigmaH_proxy = sigmaH) %>% 
  # Arrange along the plotting variables
  arrange(system_ID, KH, sigmaH_proxy, mean) %>% 
  ungroup()

# add many third proxy sigmaH points at infinity to make the values easier to see there
temp <- filter(CTmax_df, is.infinite(sigmaH)) %>%
  mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH,
                               mean(c(1.25 * infinite_divide, infinite_skew))
  ))
temp2 <- filter(CTmax_df, is.infinite(sigmaH)) %>%
  mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH,
                               mean(c(1.15 * infinite_divide, infinite_skew))
  ))
temp3 <- filter(CTmax_df, is.infinite(sigmaH)) %>%
  mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH,
                               mean(c(1.05 * infinite_divide, infinite_skew))
  ))
temp4 <- filter(CTmax_df, is.infinite(sigmaH)) %>%
  mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH,
                               mean(c(1.3 * infinite_divide, infinite_skew))
  ))
temp5 <- filter(CTmax_df, is.infinite(sigmaH)) %>%
  mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH,
                               mean(c(1.2 * infinite_divide, infinite_skew))
  ))
temp6 <- filter(CTmax_df, is.infinite(sigmaH)) %>%
  mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH,
                               mean(c(1.1 * infinite_divide, infinite_skew))
  ))
temp7 <- filter(CTmax_df, is.infinite(sigmaH)) %>%
  mutate(sigmaH_proxy = ifelse(is.finite(sigmaH), sigmaH,
                               mean(c(infinite_divide, infinite_skew))
  ))

@@

min_CTmax <- floor(min(min(CTmax_df$mean),min(CTmax_df$median)))
max_CTmax <- ceiling(max(max(CTmax_df$mean),max(CTmax_df$median)))
CTmax_breaks <- seq(min_CTmax, max_CTmax, by = 1)

CTmax_heat_plots <- CTmax_df %>%
  ## Set up plot ##
  # x = biting tolerance (with a point at infinity),
  # y = vertebrate host population density,
  # color = CTmax
  ggplot(aes(x = KH, y = sigmaH_proxy, z = median)) +
  # CTmax for FINITE sigmaH:
  geom_contour_filled(
    data = filter(CTmax_df, sigmaH_proxy < 100)
  ) +

  # CTmax for INFINITE sigmaH:
  geom_contour_filled(
    data = filter(CTmax_df, is.infinite(sigmaH))
  ) +
  # x-axis: log10-scale with no buffer space
  scale_x_log10(
    name = TeX("Vertebrate host population density (ind/ha)"),
    expand = c(0, 0),
    limits = c(0.05, 1E4),
    breaks = 10^seq(-1, 4, 1),
    labels = TeX(c("$0.1$", "$1$", "$10", "$100$", "$10^3$", "$10^4$"))
  ) +
  # y-axis: log10-scale y axis, with no buffer space
  scale_y_log10(
    name = TeX("Biting tolerance (bites per host per day)"),
    expand = c(0, 0),
    breaks = sigmaH_breaks,
    labels = sigmaH_labels
  ) +
  # color:
  scale_fill_viridis_d(
    name = "Mean critical thermal maximum (°C)",
    option = "plasma"
  ) +
  # faceting:
  facet_wrap(~system_ID, scales = "free", nrow = 2, labeller = labeller()) +
  # legend:
  guides(fill = guide_coloursteps(
    title.position = "top", title.hjust = 0.5,
    barwidth = unit(10, "cm"),
    show.limits = TRUE
  )) +
  # theme options:
  theme_minimal(16) +
  theme(
    legend.box = "horizontal",
    legend.position = "bottom",
    legend.margin = margin(0, 0, 0, 0),
    legend.title = element_text(size = 10),
    legend.direction = "horizontal",
    legend.justification = "left",
    axis.title.x = element_text(hjust = 0.5),
    strip.text = ggtext::element_markdown(
      size = 11,
      hjust = 0,
      padding = margin(0, 0, 0, 0),
      margin = margin(1, 1, 1, 1)
    )
  )

# Plot
CTmax_heat_plots <- shift_legend(CTmax_heat_plots)
```
